A compact program for 3D passive seismic source-location imaging

### 2021-07-01 passive/paper.tex
Wed Jun 30 22:35:06 CDT 2021
Thu Jul  1 11:14:43 CDT 2021

%\inputdir{field3d_geo}
%%\plot{test1}{width=\textwidth}{Separated x-component of the S1 elastic wavefield in the orthorhombic media.}
%\multiplot{4}{rsf_real,sov,f-location-tr,f-location1}{width=0.45\textwidth}{Field data example. (a) Recorded microseismic data. (b) Constructed velocity model. \dlo{(c) 3D source location image.}\wen{(c) 3D source location image using the traditional method. (d) 3D source location image using the proposed method.}}
%
%\inputdir{mod3d_geo_ng}
%\multiplot{4}{data_mask0_ng2,data_mask0_ng6,data_mask0_ng8,data_mask0_ng10}{width=0.45\textwidth}{The first group of recorded data when $N_g=2,6,8,10$, respectively. }
%
%\multiplot{4}{location1-ng2,location1-ng6,location1-ng8,location1-ng10}{width=0.45\textwidth}{The images of the first source location when $N_g=2,6,8,10$, respectively. }
%
%\inputdir{mod3d_geo_noise}
%\multiplot{4}{data-2,data-4,data-6,data-8}{width=0.45\textwidth}{Recorded data when noise variation $\sigma^2=0.01,0.5,10,50$, respectively. The corresponding S/Ns of (a)-(d) are -4.97 dB, -21.96 dB, -34.97 dB, and -41.96 dB, respectively. }
%
%\multiplot{4}{location1-noise2,location1-noise4,location1-noise6,location1-noise8}{width=0.45\textwidth}{The images of the first source location when noise variation $\sigma^2=0.01,0.5,10,50$, respectively. }
%
%%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr1.rsf 
%%   0:        -1.957
%%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr2.rsf 
%%   0:        -4.967
%%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr3.rsf 
%%   0:        -14.98
%%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr4.rsf 
%%   0:        -21.96
%%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr5.rsf 
%%   0:        -31.96
%%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr6.rsf 
%%   0:        -34.97
%%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr7.rsf 
%%   0:        -37.98
%%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr8.rsf 
%%   0:        -41.96
%%  
%
%\inputdir{mod3d_geo_density}
%\multiplot{4}{data-d6,data-d8,data-d9,data-d10}{width=0.45\textwidth}{The observed data with 121, 81, 16, and 8 recorded traces, respectively.  }
%
%\multiplot{4}{location1-density6,location1-density8,location1-density9,location1-density10}{width=0.45\textwidth}{The images of the first source location when there are 121, 81, 16, and 8 recorded traces, respectively. }
% 
\bibliographystyle{seg}
\bibliography{micro}

>>>>

\inputdir{field3d}
%\plot{test1}{width=\textwidth}{Separated x-component of the S1 elastic wavefield in the orthorhombic media.}
\multiplot{4}{rsf_real,sov,f-location-tr,f-location1}{width=0.45\textwidth}{Field data example. (a) Recorded microseismic data. (b) Constructed velocity model. \dlo{(c) 3D source location image.}\wen{(c) 3D source location image using the traditional method. (d) 3D source location image using the proposed method.}}

\inputdir{mod3d_ng}
\multiplot{4}{data_mask0_ng2,data_mask0_ng6,data_mask0_ng8,data_mask0_ng10}{width=0.45\textwidth}{The first group of recorded data when $N_g=2,6,8,10$, respectively. }

\multiplot{4}{location1-ng2,location1-ng6,location1-ng8,location1-ng10}{width=0.45\textwidth}{The images of the first source location when $N_g=2,6,8,10$, respectively. }

\inputdir{mod3d_noise}
\multiplot{4}{data-2,data-4,data-6,data-8}{width=0.45\textwidth}{Recorded data when noise variation $\sigma^2=0.01,0.5,10,50$, respectively. The corresponding S/Ns of (a)-(d) are -4.97 dB, -21.96 dB, -34.97 dB, and -41.96 dB, respectively. }

\multiplot{4}{location1-noise2,location1-noise4,location1-noise6,location1-noise8}{width=0.45\textwidth}{The images of the first source location when noise variation $\sigma^2=0.01,0.5,10,50$, respectively. }
%
%%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr1.rsf 
%%   0:        -1.957
%%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr2.rsf 
%%   0:        -4.967
%%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr3.rsf 
%%   0:        -14.98
%%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr4.rsf 
%%   0:        -21.96
%%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr5.rsf 
%%   0:        -31.96
%%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr6.rsf 
%%   0:        -34.97
%%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr7.rsf 
%%   0:        -37.98
%%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr8.rsf 
%%   0:        -41.96
%%  
%
\inputdir{mod3d_density}
\multiplot{4}{data-d6,data-d8,data-d9,data-d10}{width=0.45\textwidth}{The observed data with 121, 81, 16, and 8 recorded traces, respectively.  }

\multiplot{4}{location1-density6,location1-density8,location1-density9,location1-density10}{width=0.45\textwidth}{The images of the first source location when there are 121, 81, 16, and 8 recorded traces, respectively. }
% 
\bibliographystyle{seg}
\bibliography{micro}
